Notes on Wide Gap

### 2016-02-27 paper/wide_gap_notes.tex
z component of Psi equation
rhat momentum equation
LHS of Psi equation

1. Find x and z components of the momentum equation, i.e.:

@@

Which becomes

\beq
\frac{1}{r^2} \partial_t \partial_r \Psi
\eeq

>>>>

1. Find $\rhat$ and $\zhat$ components of the momentum equation, i.e.:

@@

We sub in our stream/flux function notation and expand the operators in cylindrical coordinates. Then take $\partial_r$ of the resulting equation to obtain:

\begin{multline}
\frac{1}{r^2} \partial_t \partial_r \Psi - \frac{1}{r} \partial_t \partial_r^2 \Psi - \frac{3}{r^4}\partial_z \Psi \partial_r \Psi + \frac{1}{r^3} \partial_r \left( \partial_z \Psi \partial_r \Psi \right) + \frac{2}{r^3} \partial_z \Psi \partial_r^2 \Psi - \frac{1}{r^2} \partial_r \left(\partial_z \Psi \partial_r^2 \Psi \right)\\
- \frac{2}{r^3} \partial_r \Psi \partial_r\partial_z \Psi + \frac{1}{r^2} \partial_r \left(\partial_r \Psi \partial_r \partial_z \Psi\right) = \\
\partial_r\left(B_\theta \partial_z B_\theta\right) + \frac{2}{r^3} \partial_z^2 A \partial_z A - \frac{1}{r^2} \partial_r \left(\partial_z^2 A \partial_z A\right) + \frac{3}{r^4} \partial_z A \partial_r A - \frac{1}{r^3} \partial_r \left(\partial_z A \partial_r A \right) - \frac{2}{r^3} \partial_z A \partial_r^2 A \\
+ \frac{1}{r^2} \partial_r \left(\partial_z A \partial_r^2 A \right) 
+ \frac{1}{\reye} \left[\frac{3}{r^4} \partial_r \Psi - \frac{3}{r^3} \partial_r^2 \Psi + \frac{2}{r^2} \partial_r^3 \psi - \frac{1}{r} \partial_r^4 \Psi\right]
\end{multline}

Repeat this process for the $\rhat$ component of the momentum equation,

\beq
\partial_t u_r + \left[u \cdot \nabla u \right]_r = \left[ \left( \nabla \times B \right) \times B \right]_r + \frac{1}{\reye}\left[ \nabla^2 u \right] _r
\eeq

and take $\partial_z$ of the expanded equation to obtain

\begin{multline}
\frac{1}{r} \partial_t \partial_z^2 \Psi - \frac{1}{r^3} \partial_z \left(\partial_z \Psi \partial_z \Psi\right) + \frac{1}{r^2} \partial_z\left(\partial_z\Psi \partial_z\partial_r \Psi\right) - \frac{1}{r^2} \partial_z \left(\partial_r \Psi \partial_z^2 \Psi\right) - \frac{1}{r} 2 u_\theta \partial_z u_\theta \\
= - \frac{1}{r^2} \partial_z^3 A \partial_r A - \frac{1}{r^2} \partial_z^2 A \partial_r \partial_z A + \frac{2}{r^3} \partial_r\partial_z A \partial_r A - \frac{1}{r^2} \partial_r^2 \partial_z A \partial_rA - \frac{1}{r^2} \partial_r^2 A \partial_r \partial_z A
\end{multline}

It is clear from the $\partial_t$ terms that we must combine these equations by subtracting the $\zhat$ equation from the $\rhat$ equation.

When we do, we can simplify the LHS of the equation to:

\beq
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\theta \partial_z u_\theta
\eeq

Note that the relevant quantity appears to be $\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi$, and that the $\frac{1}{r^2}$ in the second term cannot come out of the Jacobian (a point of disagreement with Jeff's equation above).
